### 2015-10-28 postdoctoral/gamma_functions.tex
broke compactness sadface :-(

  \begin{definition}
    For any LOS \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-open subsets of \(L\) (leftward subsets which are open)
    linearly ordered by \(\subseteq\).
  \end{definition}

@@

  \begin{proof}
    Each subset \(S\) has a supremum \(\cup S\) and infimum \(\cap S\)
    (or \(\int(\cap S)\)).
  \end{proof}

  Note that \(\check L\)
  this is not a ``compactification'' as \(L\) does not necessarily
  embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
  \(t\mapsto [0,t)\), but then note that the subspace topology induces the
  reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
  However \(\hat L\) is basically
  the typical way of compactifying a linearly ordered space \(L\) (actually,
  left-closed is more typical, but this works similarly and fits our applications
  later),
  provided \(L\) lacks a maximum element (otherwise the whole space is an [easily
  removable] isolated point in \(\hat L\)).

@@

@@

  \begin{proof}
    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \nu, L\}\) with
    the linear order described above. We claim that if \(\phi\) is the
    characteristic function for a subset of \(L\), then \(\int\circ\phi\)
    is an order isomorphsim between \(\<Y,\leq\>\) and
    \(\<\hat L,\subseteq\>\).

    Let \(A\) be a left-open subset of \(L\). Then let \(\vect x(a)=1\) when
    \(a\in\cl A\) and \(0\) otherwise. Then \(\vect x\in Y\),
    \(\phi(\vect x)=\cl A\), and \(\int\circ\phi(\vect x)=\int\cl A=A\).

    Let \(\vect x,\vect y\in Y\). If
    \(\int\circ\phi(\vect x)=\int\circ\phi(\vect y)=A\), then \(A\) is a
    left-open set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\). It follows
    that if \(b\in\cl A\), then as \(\vect x,\vect y\in Y\),
    \(\vect x(b)=\vect y(b)=1\) as well. And if \(c\not\in\cl A\), then
    as \(c\not\in\phi(x)\),
    \(\vect x(c)=\vect y(c)=0\), so \(\vect x=\vect y\).

    Finally let \(\vect x<\vect y\), so there exists \(a\in L\) with
    \(\vect x(a)=0,\vect y(a)=1\). Then
    \(
      \int\circ\phi(\vect x)
        \subseteq
      \phi(\vect x)
        \subseteq
      (\leftarrow,a)
        \subseteq
      \int\circ\phi(\vect y)
    \). Thus \(\int\circ\phi\) preserves order.
  \end{proof}

  \begin{corollary}
    \(
      \varprojlim \{2, \nu, \alpha\}
      \cong
      \varprojlim^\star \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    Since \(\hat\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \nu, \alpha\}
      \cong \hat\alpha =
    \alpha+1\) for free. Then observe that all leftward sets in \(\alpha\) are
    open: \(A=[0,\min(\alpha+1\setminus A))\).
    Thus we have
    \(\varprojlim \{2, \nu, \alpha\}\cong\check\alpha=\hat\alpha=\alpha+1\).
  \end{proof}

  \begin{theorem}
    Let \(M\) be a LOTS with minimum \(0\).
    \(Z=\varprojlim^\star \{M, \nu, L\}\cong \{-\infty\}\cup \hat L\lexTimes M'\)
    where \(M'=M\setminus\{0\}\),
    \(\lexTimes\) induces the lexicographic ordering on the product,
    and \(-\infty\) is a least element.
  \end{theorem}

  \begin{proof}
    Let \(\rho(\vect x)=\int\{a\in L:\exists b> a(\vect x(b)>0)\}\);
    this is obviously leftwards, and it's open since for each
    \(a\in\rho(\vect x)\), \(a\in(\leftarrow,b)\subseteq\rho(\vect x)\).
    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
    \(\rho(\vect x)=\rho(\vect y)\)
    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

@@

    We first show that \(r\) is a bijection. Let \(A\) be left-open
    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise.
  \end{proof}

>>>>

  \begin{definition}
    For any LOS \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-closed subsets of \(L\) (leftward subsets which are closed)
    linearly ordered by \(\subseteq\).
  \end{definition}

@@

  \begin{proof}
    Each subset \(S\) has an infimum \(\cap S\) and a supremum \(\cup S\)
    (or \(\cl(\cap S)\)).
  \end{proof}

  Note that \(\check L\)
  is not a ``compactification'' as \(L\) does not necessarily
  embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
  \(t\mapsto [0,t)\), but then note that the subspace topology induces the
  reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
  However \(\hat L\) is
  the typical way of compactifying a linearly ordered space \(L\),
  provided \(L\) lacks a least element (otherwise the empty set is an [easily
  removable] isolated point in \(\hat L\)).

@@

  \begin{corollary}
    \(
      \varprojlim \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \nu, \alpha\}
      \cong \check\alpha =
    \alpha+1\) for free.
  \end{proof}

@@

  \begin{proof}
    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \nu, L\}\) with
    the linear order described above. We claim that if \(\phi\) is the
    characteristic function for a subset of \(L\), then \(\phi\)
    is an order isomorphsim between \(\<Y,\leq\>\) and
    \(\<\hat L,\subseteq\>\).

    Let \(A\) be a left-closed subset of \(L\). Let \(\vect x(a)=1\) when
    \(a\in A\) and \(\vect x(a)=0\) otherwise. Then \(\vect x\in Y\) and
    \(\phi(\vect x)=A\).

    Let \(\vect x,\vect y\in Y\). If
    \(\phi(\vect x)=\phi(\vect y)=A\), then \(A\) is a
    left-closed set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\)
    and \(\vect x(a)=\vect y(a)=0\) otherwise, so \(\vect x=\vect y\).

    Finally let \(\vect x<\vect y\), so there exists \(a\in L\) with
    \(\vect x(a)=0\), \(\vect y(a)=1\). Then
    \(
      \phi(\vect x)
        \subseteq
      (\leftarrow,a)
        \subseteq
      \phi(\vect y)
    \). Thus \(\phi\) preserves order.
  \end{proof}

  \begin{corollary}
    \(
      \varprojlim^\star \{2, \nu, \alpha\}
      \cong
      \alpha+1
    \)
    for every infinite limit or finite ordinal \(\alpha\).
  \end{corollary}

  \begin{proof}
    If \(\alpha\) is finite, then of course all (leftward) sets are
    closed and we get \(\hat\alpha=\check\alpha=\alpha+1\) for free.
    Otherwise, since \(\alpha\) lacks a greatest point, \(\hat\alpha\)
    is homeomorphic to its usual compactification \(\alpha+1\).
  \end{proof}

  In fact, \(\hat\alpha=\alpha+1\setminus L(\alpha)\) where \(L(\alpha)\)
  is the colleciton of all limit ordinals less than \(\alpha\), which also
  shows \(\hat\alpha\cong\alpha\) for infinite successor ordinals \(\alpha\).

  \begin{theorem}
    Let \(M\) be a LOTS with minimum \(0\).
    \(
      Z
        =
      \varprojlim^\star \{M, \nu, L\}
        \cong
      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
    \)
    where \(M'=M\setminus\{0\}\),
    \(\lexTimes\) induces the lexicographic ordering on the product,
    and \(-\infty\) is a least element.
  \end{theorem}

  \begin{proof}
    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
    \(\rho(\vect x)=\rho(\vect y)\)
    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).

@@

    We first show that \(r\) is a bijection. Let \(A\) be left-closed
    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
    is similarly trivial.

    Finally let \(\vect 0<\vect x<\vect y\).
    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
  \end{proof}

  This gives us the previous result as a corollary:
  \(
    \varprojlim^\star \{2, \nu, L\}
      \cong
    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
      \cong
    \hat L
  \). Unfortunately, the result is not always compact.

  \begin{example}
    \(
      \varprojlim^\star \{I, \nu, I\}
        \cong
      \{-\infty\}\cup (0,1]\lexTimes(0,1]
    \)
  is not compact.
  \end{example}

  \begin{proof}
    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
    is closed discrete.
  \end{proof}
